\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}
\usepackage{lineno} % add
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\bibliographystyle{elsarticle-harv}
\biboptions{sort&compress} % For natbib
\usepackage{graphicx}
\usepackage{booktabs} % book-quality tables
%% Redefines the elsarticle footer
%\makeatletter
%\def\ps@pprintTitle{%
% \let\@oddhead\@empty
% \let\@evenhead\@empty
% \def\@oddfoot{\it \hfill\today}%
% \let\@evenfoot\@oddfoot}
%\makeatother

% A modified page layout
\textwidth 6.75in
\oddsidemargin -0.15in
\evensidemargin -0.15in
\textheight 9in
\topmargin -0.5in
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Predicting Food Insecurity with Machine Learning based on readily avaliable data},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}
% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}
% Pandoc header


\usepackage[nomarkers]{endfloat}

\begin{document}
\begin{frontmatter}

  \title{Predicting Food Insecurity with Machine Learning based on readily
avaliable data}
    \author[University Of Illinois At Urbana-Champaign]{Yujun Zhou\corref{c1}}
   \ead{zhou100@illinois.edu} 
   \cortext[c1]{Corresponding Author}
      \address[University Of Illinois At Urbana-Champaign]{Department of Agriculture and Consumer Economics, University of
Illinois, USA}
  
  \begin{abstract}
  We determine whether corn and soybean futures contract prices are
  stationary or not.
  \end{abstract}
   \begin{keyword} prices, unit root, stationarity \sep \end{keyword}
 \end{frontmatter}

Temporal Poverty Prediction using Satellite Imagery(Chen 2017).

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  measuring and tracking areas of poor is a necessary step for targeting
  aid and guiding policy decisions.
\item
  obtaining data is time and labor intensive
\item
  (Blumenstock 2016)
\end{enumerate}

\section{Methods}\label{methods}

\subsection{Participants}\label{participants}

\subsection{Material}\label{material}

\subsection{Procedure}\label{procedure}

\subsection{Data analysis}\label{data-analysis}

We used for all our analyses.

\section{Results}\label{results}

\section{Discussion}\label{discussion}

\newpage

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\hypertarget{ref-blumenstock2016fighting}{}
Blumenstock, J. E. 2016. ``Fighting poverty with data.'' \emph{Science}
353 (6301). American Association for the Advancement of Science:
753--54.
doi:\href{https://doi.org/10.1126/science.aah5217}{10.1126/science.aah5217}.

\hypertarget{ref-chentemporal}{}
Chen, Derek. 2017. ``Temporal Poverty Prediction using Satellite
Imagery.''

\end{document}


